---
title: "Final Project - Twitter"
author: "Kushagra Sen, DeepakRao Bandhakavi, Akhil Menon"
date: "2/24/2020"
output: html_document
---
In this project, we are analyzing the sentiments towrads the iPhone 11 Series.
The data set has got over 20,000 tweets spread across a span of ~ first 20 days of January 2020.

The process started with extracting tweets from twitter using Twitter API. The tweets are collected by filtering from frequently used hashtags like #iPhone11, #iPhone11Pro etc. and famous twitter handles such as the Apple CEO Tim Cook. 

Post collection, data is cleaned to make it devoid of duplicates, punctuation flaws, numbers, URL’s etc which cleared the ground for data analysis. 


```{r setup, include=FALSE}
library(twitteR)
library(rtweet)
library(stringr)
library(rvest)
library(xml2)
library(dplyr)
library(tidyverse)
library(tidytext)
library(xlsx)
library(textclean)
library(qdapRegex)
library(tm)
library(SnowballC)
library(scales)
library(ggplot2)
library(wordcloud)
library(udpipe)
library(lattice)
library(wordcloud2)
library(lattice)
library(NLP)
library(textdata)
library(rlang)
library(RColorBrewer)
library(reshape2)
library(igraph)
library(ggraph)
library(topicmodels)
```

```{r}
final_tweets <- read.csv("https://drive.google.com/uc?export=download&id=1kOlxzs8Bq9WzXl8UlZDD8mOrTE9pyq6s")
head(final_tweets,5)
```

We have date written in a format MM/DD/YYYY and we are de-limiting it so that we can evaluate the monthly and yearly trends.

```{r}
final_tweets <- final_tweets %>%
  separate(created_at
           , into = c("Month", "Date", "Year"), sep = "/")
```

### **Step 1:** Data Visualization

**This graph shows the frequency of tweets based on the Source attribute**

```{r}
src_df <- table(final_tweets$source)
str(src_df)
w <- as.data.frame(table(final_tweets$source))
w <- w[order(-w$Freq),]
names(w) <- c("Source","Frequency")
ggplot(data=w[0:10,], aes(x=reorder(Source,-Frequency), y=Frequency)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=Frequency), vjust=-0.3, size=3.5)+
  theme_minimal()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) +xlab("Source")

```

**This graph shows the frequency of tweets based on the user location**

```{r}
w <- as.data.frame(table(final_tweets$country ))
w <- w[order(-w$Freq),]
names(w) <- c("Country","Frequency")

ggplot(data=w[0:10,], aes(x=reorder(Country,-Frequency), y=Frequency)) +
  geom_bar(stat="identity", fill="orange")+
  geom_text(aes(label=Frequency), vjust=-0.3, size=3.5)+
  theme_minimal()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) +xlab("Source")

```

**Here we can see the Day-to-Day trend of tweets regarding iPhone 11 series**

```{r}
pie <- ggplot(final_tweets, aes(x = "", fill = factor(Date))) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Day to Day trend of tweets regarding iPhone 11 series", 
       caption="Data has been pulled using Twitter API ")
pie + coord_polar(theta = "y", start=0)
```


### **Step 2:** Sentiment Analysis

**1. Cleaning the special characters and links from the tweets:**
Since the data obtained from twitter is random text with a lot of irregularities and irrelevant content, data had to be made ready for further analysis. The tweets consisted of duplicate tweets, additional website/blog links, Punctuation marks, irregular font and text, repeated words.

```{r}
total_text <- rbind(final_tweets)
total_text$text = gsub("&amp", "", total_text$text)
total_text$text = gsub("&amp", "", total_text$text)
total_text$text = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", total_text$text)
total_text$text = gsub("@\\w+", "", total_text$text)
total_text$text = gsub("[[:punct:]]", "", total_text$text)
total_text$text = gsub("[[:digit:]]", "", total_text$text)
total_text$text = gsub("http\\w+", "", total_text$text)
total_text$text = gsub("[ \t]{2,}", "", total_text$text)
total_text$text = gsub("^\\s+|\\s+$", "", total_text$text)
```

Frequently occuring but common words which can be considered as stop words

```{r}
df <- total_text %>% mutate(Text = str_replace_all(text, "(<br />)+", " "))
tokens <- df %>% unnest_tokens(output = word, input = Text)
tokens %>%  dplyr::count(word, sort = TRUE)
```

As most of the words are stopwords, we should remove them.

```{r}
get_stopwords()
cleaned_tokens <- tokens %>%  anti_join(get_stopwords())
nums <- cleaned_tokens %>% filter(str_detect(word, "^[0-9]")) %>% select(word) %>% unique()
cleaned_tokens <- cleaned_tokens %>%   anti_join(nums, by = "word")
```

After removing the stop words, we get:

```{r}
cleaned_tokens %>%  dplyr::count(word, sort = TRUE)
```

**2. Word Cloud of positive and negative words:**
This is a word cloud showing the **positive** and **negative** words whose frequency is greater than 200 

```{r}
tokens %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort=TRUE) %>%
  acast(word ~ sentiment, value.var="n", fill=0) %>%
  comparison.cloud(colors=c("#F8766D", "#00BFC4"), max.words=200)

sentiments <- tokens %>% 
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort=TRUE) 
```


**3. This graph shows the frequency of various sentiments gathered through these tweets**

```{r}
sentiments <- tokens %>% 
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort=TRUE) 

ggplot(data=sentiments, aes(x=reorder(sentiment, n, sum), y=n)) + 
  geom_bar(stat="identity", aes(fill=sentiment), show.legend=FALSE) +
  labs(x="Sentiment", y="Frequency") +
  theme_bw() +
  coord_flip()
```

**4. This graph shows the Top 10 frequent terms for each sentiment**

```{r}
sentiments %>%
  group_by(sentiment) %>%
  arrange(desc(n)) %>%
  slice(1:10) %>%
  ggplot(aes(x=reorder(word, n), y=n)) +
  geom_col(aes(fill=sentiment), show.legend=FALSE) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  facet_wrap(~sentiment, scales="free_y") +
  labs(y="Frequency", x="Words") +
  coord_flip()
```


**5. This graph shows the frequency of words in the cleaned tokens which we obtained after removing the rare words**

```{r}
cleaned_tokens %>%   dplyr::count(word, sort = T) %>%  dplyr::rename(word_freq = n) %>%  
  ggplot(aes(x=word_freq)) +  geom_histogram(aes(y=..count..), color="black", fill="red", alpha=0.3, bins=20) +  scale_x_continuous(breaks=c(0:5,10,100,500,10e3), trans="log1p", expand=c(0,0)) +  scale_y_continuous(breaks=c(0,100,1000,5e3,10e3,5e4,10e4,4e4), expand=c(0,0)) +  theme_bw() 

```

So it makes sense to remove rare words to improve the performance of text analytics.
Let's remove words that have less than 10 appearances in our collection:

```{r}
rare <- cleaned_tokens %>%   dplyr::count(word) %>%  filter(n<10) %>%  select(word) %>% unique()
cleaned_tokens <- cleaned_tokens %>%   anti_join(rare, by = "word")
length(unique(cleaned_tokens$word))
```

**6. Word Cloud of frequently occuring words**

```{r}
pal <- brewer.pal(8,"Dark2")
cleaned_tokens %>%   dplyr::count(word) %>%  with(wordcloud(word, n, random.order = FALSE, max.words =500, colors=pal))
```


**7. Getting Sentiments from "nrc","afinn" and "bing"**

```{r}
get_sentiments("nrc")
get_sentiments("afinn")
get_sentiments("bing")
sent_reviews = cleaned_tokens %>%
  left_join(get_sentiments("nrc")) %>%
  rename(nrc = sentiment) %>%
  left_join(get_sentiments("bing")) %>%
  rename(bing = sentiment) %>%
  left_join(get_sentiments("afinn")) %>%
  rename(afinn = value)
head(sent_reviews,5)
```

**8. Most common positive and negative words**

```{r}
bing_word_counts <- sent_reviews %>%  filter(!is.na(bing)) %>%  dplyr::count(word, bing, sort = TRUE)

bing_word_counts %>%  filter(n > 200) %>%  mutate(n = ifelse(bing == "negative", -n, n)) %>%
  mutate(word = reorder(word, n)) %>%  ggplot(aes(word, n, fill = bing)) +  geom_col() +  coord_flip() +  labs(y = "Contribution to sentiment")

```

**9. Now, tokenizing by n-gram**

```{r}
bigrams <- tokens %>%  unnest_tokens(bigram, text, token = "ngrams", n = 2)
bigrams %>%  dplyr::count(bigram, sort = TRUE)
```

**10. Filtering the bi-grams**

```{r}
bigrams_separated <- bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)
```

**New bi-gram counts:**
```{r}
bigrams_filtered %>% count(word1, word2, sort = TRUE)
```

**11. Visualizing the bi-grams:**

```{r}
bigram_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigram_counts <- bigram_united %>% 
  dplyr::count(bigram, sort = TRUE)

bigram_counts %>% arrange(desc(n))%>% head(20)%>%ggplot(aes(x=factor(bigram,levels=bigram),y=n))+geom_bar(stat="identity",fill="#003E45")+labs(title="Top 20 bigram words in Comments")+coord_flip()
```

**12. Word correlations**

```{r}
rare <- cleaned_tokens %>%
  count(word) %>%
  filter(n<100) %>% #remove rare words
  # < 1000 reviews
  select(word) %>% distinct()

word_cor <- cleaned_tokens %>%
  filter(!word %in% rare$word) %>%
  widyr::pairwise_cor(word, Sno) %>%
  filter(!is.na(correlation),
         correlation > .25)
head(word_cor,5)
```

**Visualizing word correlation:**
```{r}
word_cor %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 6) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()
```

**13. Document Term Matrix**

tf-idf is Term Frequency and Inverse document frequency. Using this, We can see the repititon of a term in a document and as compared to overall frequency of document.


```{r}
word_counts_by_SNo <- cleaned_tokens %>%  
  group_by(Sno) %>%  
  dplyr::count(word, sort = TRUE)
word_counts_by_SNo

review_dtm <- word_counts_by_SNo %>%
  cast_dtm(Sno, word, n)
```

**14. Displaying the top tf-idf in the document**

```{r}
tfidf <- word_counts_by_SNo %>%  
  bind_tf_idf(word, Sno, n) 

top_tfidf <- tfidf %>%
  group_by(Sno) %>%
  arrange(desc(tf_idf)) %>%
  top_n(3) %>% ungroup() %>%
  arrange(Sno, -tf_idf) 
head(top_tfidf,10)
```

**15. Now creating a 5 topic LDA model**

```{r}
lda5 <- LDA(review_dtm, k = 5, control = list(seed = 1234))
terms(lda5, 10)
```
























































































































